Word Sense Disambiguation: Pipelining with Supervised LSA

### 2014-05-11 paper.tex
Update tables

	\subsection{POS Bigram Model}
	POS Bigram Model (w/frequency count > 3)

	Threshold	$80\%	40\%	0\%$
	Correctly identified	$199	518	574$
	Total identified	$253	893	1136$
	$\%$ Accuracy	$78.7\%	58.0\%	50.5\%$
	$\%$ Coverage	$5.8\%	20.6\%	26.2\%$

	POS Bigram Model (w/frequency count > 0)

	Threshold	$80\%	40\%	0\%$
	Correctly identified	$466	808	850$
	Total identified	$898	1641	1826$
	$\%$ Accuracy	$51.9\%	49.2\%	46.5\%$
	$\%$ Coverage	$20.7\%	38.7\%	42.2\%$

>>>>

	\subsection{POS Bigram Model}

	POS Bigram Model (w/frequency count $>$ 3): 
	\begin{table}[h]
	\begin{tabular}{|l|l|l|l|}
	\hline
	Threshold            & 80\%   & 40\%   & 0\%    \\ \hline
	Correctly identified & 199    & 518    & 574    \\ \hline
	Total identified     & 253    & 893    & 1136   \\ \hline
	\% Accuracy          & 78.7\% & 58.0\% & 50.5\% \\ \hline
	\% Coverage			 & 5.8\%  & 20.6\% & 26.2\% \\ \hline
	\end{tabular}
	\end{table}\\
	POS Bigram Model (w/frequency count $>$ 0)
	\begin{table}[h]
	\begin{tabular}{|l|l|l|l|}
	\hline
	Threshold            & 80\%   & 40\%   & 0\%    \\ \hline
	Correctly identified & 466    & 808    & 850    \\ \hline
	Total identified     & 898    & 1641   & 1826   \\ \hline
	\% Accuracy          & 51.9\% & 49.2\% & 46.5\% \\ \hline
	\% Coverage          & 20.7\% & 38.7\% & 42.2\% \\ \hline
	\end{tabular}
	\end{table}
